%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{University Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%========================== ACC ==========================
%---------------------------------------------------------
  \cventry
    {Carnegie Mellon University} % Organisation
    {Parallel Four-color Map Solver} % Project
    {Pittsburgh, PA} % Location
    {May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Negotiated and collaborated with teammates on the interactive web client interface (JavaScript, HTML, CSS) 
        using P5.js. Built a server (C++) on the backend cluster that communicates with web client through HTTP.}
        \item {Innovated and implemented parallel breadth-first-search algorithm (C++) using OpenMP that minimizes 
        inter-node dependencies and cache false-sharing. Achieved super-linear scaling (more than 10x speedup) on 
        a cluster of 8 nodes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Carnegie Mellon University} % Organisation
    {Apache Spark Interative Machine Learning Training} % Project
    {Pittsburgh, PA} % Location
    {Apr 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a distributed logistic regression algorithm (Python) in Apache Spark that leverages 
        sparse linear algebra and join-based communication between distributed dataset. Deployed on a cluster 
        of 16 nodes and trained excessively huge models within reasonable time limits.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Carnegie Mellon University} % Organisation
    {AWS Auto-Scaling Design} % Project
    {Pittsburgh, PA} % Location
    {Mar 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Designed an AWS auto-scaling controller (deployed via Terraform) that automatically 
        collects workload metrics and adjust the number of running EC2 instances. The controller 
        increases aggregate request processing speed by twice, while decreases the a ggregate EC2 
        cost by 7\%.}
      \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Carnegie Mellon University} % Organisation
%     {Intelligent Job Scheduler in Kubernates} % Project
%     {Pittsburgh, PA} % Location
%     {May 2023} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of project
%         \item {Implemented a Kubernates job scheduler (Go) using Kube Batch for randomly arriving jobs with 
%         different scheduling preferences. Deployed on a multi-rack data cluster consisting of heterogeneous 
%         hardwares, and achieved more than 3 times improvements compared to default scheduler in terms of average
%         job completion time.}
%       \end{cvitems}
%     }

%========================== 17514 ==========================
%---------------------------------------------------------
  \cventry
    {Carnegie Mellon University} % Organisation
    {Santorini Game Development} % Project
    {Pittsburgh, PA} % Location
    {Nov 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a board game called Santorini, using Java for backend, and Typescript \& ReactJS for 
        frontend.}
        \item {Designed HTTP-based RESTful APIs between backend and frontend to achieve low-coupling and 
        high cohesion of the entire program.}
        \item {Deviced flexible framework interface in backend that allows users to add their own card plugins 
        by implementing just a few lines of codes.}
      \end{cvitems}
    }
%========================== DS ==========================

\end{cventries}